Trans-dimensional Bayesian Inference and Nested Sampling

### 2015-01-25 Documents/Talk/content.tex
Projects
Wokring on the talk

@@

@@

\begin{frame}[t]{Sinusoid data movie}

@@

>>>>

\begin{frame}[t]{Motivating Problem I}
Problems like this arise both inside and outside of astronomy,
for example:
\vspace{20pt}
\begin{itemize}
\item Asteroseismology
\item Extrasolar planets (radial velocity technique)
\end{itemize}
\end{frame}

@@

\begin{frame}[t]{Motivating Problem II}
This is a fundamental task in astronomy!
\end{frame}

@@

\begin{frame}[t]{Sinusoid data movie}
{\tt https://www.youtube.com/watch?v=q4s8NJyUVoY}
\end{frame}

@@

\begin{frame}[t]{Real projects}
\begin{itemize}
\item Magnetar bursts
\item Making probabilistic catalogs
\item Gravitational lens time delays in unresolved systems
\item Gravitational lens inversion
\item Modelling the progress of parallel Nested Sampling runs (!)
\end{itemize}
\end{frame}
